Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-05-13 tese2/evaluation.tex
gonna sleep

    \includegraphics[width=\textwidth]{figures/test_ui_01.png}
        a) Friend list path
\label{fig:minipage1}
\end{minipage}
\begin{minipage}[b]{0.35\linewidth}
    \centering

    \includegraphics[width=\textwidth]{figures/test_ui_02.png}
         b) Friend requests path
\label{fig:minipage2}
\end{minipage}
\begin{minipage}[b]{0.2\linewidth}
    \centering

    \includegraphics[width=\textwidth]{figures/test_ui_03.png}
         c) Search bar path
\label{fig:minipage2}
\end{minipage}

@@

From the data that we have collected, namely the task duration (Figure \ref{fig:user_times}), number of clicks (Figure \ref{fig:user_clicks}), number of errors (Figure \ref{fig:user_errors}), task difficulty (Figure \ref{fig:user_diffs}) and qualitative evaluation (Figure \ref{fig:user_evals}), we have calculated the confidence intervals in order to understand the most plausible values for each metric.

@@

Where $\alpha=0.05$ \footnote{95\% ($\alpha=0.05=1-0.95$) is a common value, used by researchers, to calculate confidence intervals}, $n$ is the number of samples (which may not coincide with the number of tests due to failed tasks), $\bar{x}$ is the sample mean, $x_i$ is the sample value and $s$ is the sample standard deviation that is given by:
\begin{equation}
s=\sqrt{\frac{1}{n-1}\Sigma^{n}_{i=1}(x_i-\bar{x})^2}
\end{equation}

>>>>

    \includegraphics[width=\textwidth]{figures/test_ui_01.png}
        a) Friend list path
\end{minipage}
\begin{minipage}[b]{0.35\linewidth}
    \centering

    \includegraphics[width=\textwidth]{figures/test_ui_02.png}
         b) Friend requests path
\end{minipage}
\begin{minipage}[b]{0.2\linewidth}
    \centering

    \includegraphics[width=\textwidth]{figures/test_ui_03.png}
         c) Search bar path
\end{minipage}

@@

From the data collected with twenty tests with users, namely the task duration (Figure \ref{fig:user_times}), number of clicks (Figure \ref{fig:user_clicks}), number of errors (Figure \ref{fig:user_errors}), task difficulty (Figure \ref{fig:user_diffs}) and qualitative evaluation (Figure \ref{fig:user_evals}), we have calculated the confidence intervals in order to understand the most plausible values for each metric.

@@

The youngest and oldest testers were, receptively, twenty two and thirty eight years old. Figure \ref{fig:user_ages} the ages of the users that tested our system.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{stats/user_ages.eps}
  \caption{Ages of the users that tested our system}
  \label{fig:user_ages}
\end{figure}

Where $\alpha=0.05$ \footnote{95\% ($\alpha=0.05=1-0.95$) is a common confidence level value used, by researchers, to calculate confidence intervals}, $n$ is the number of samples (which may not coincide with the number of tests due to failed tasks), $\bar{x}$ is the sample mean, $x_i$ is the sample value and $s$ is the sample standard deviation that is given by:
\begin{equation}
s=\sqrt{\frac{1}{n-1}\Sigma^{n}_{i=1}(x_i-\bar{x})^2}
\end{equation}
